---
title: "Macro Project: Blizzard Stock"
output:
  prettydoc::html_pretty:
    theme: lumen
    df_print: paged
---

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(prettydoc)
library(quantmod)
library(scales)

```

This data consists of opens, closes, volumes, adjusted closes, from 2017 - 2022. Need to adjust data to work for regression as linear regression cannot directly take time-series data.
```{r}
ATVI_Data <- read.csv("BlizzardStocks_5Y.csv")
ATVI_Data <- ATVI_Data %>% mutate(id = row_number())
ATVI_Data$Date <- as.Date(ATVI_Data$Date)

glimpse(ATVI_Data)
summary(ATVI_Data)
```

This data starts at 2017-03-31 and ends 2022-03-30
```{r}
min(ATVI_Data$Date)
max(ATVI_Data$Date)
```



# Linear Regression
Looking at monthly close prices vs the time index
```{r}
ATVI_Reg <- lm(ATVI_Data$Close ~ ATVI_Data$id)

summary(ATVI_Reg)
p1 <- plot(ATVI_Reg)
```

# Visualize linear regression
```{r}
p2 <- ggplot(data=ATVI_Data, mapping = aes(id, Close))+
  geom_point(color = "red") +
  geom_smooth(method = "lm", color = "black")+
  labs(x="Monthly Time Index starting at 2017-03-31", y = "ATVI Close")

plot(p2)
```

# Two moving averages for the stock price, 10 day window and 30 days
```{r}
ATVI_mm <- subset(ATVI_Data, index(ATVI_Data) >= "2017-03-31")

ATVI_mm10 <- rollmean(ATVI_mm[,6], 10, fill = list(NA, NULL, NA), align = "right")
ATVI_mm30 <- rollmean(ATVI_mm[,6], 30, fill = list(NA, NULL, NA), align = "right")

ATVI_mm$mm10 <- coredata(ATVI_mm10)
ATVI_mm$mm30 <- coredata(ATVI_mm30)
```



# Plotting the price and moving averages for all days since 2017
```{r}
ATVI_mm %>% 
  ggplot(aes(x = Date)) +
  geom_line(aes(y = ATVI_mm[,6], color = "ATVI")) + ggtitle("ATVI prices ") +
  geom_line(aes(y = mm10, color = "MM10")) +
  geom_line(aes(y = mm30, color = "MM30")) + xlab("Date") + ylab("Price")
```


